% LaTeX source of my resume
% =========================

% Commented for easy reuse... ;)

% See the `README.md` file for more info.

% This file is licensed under the CC-NC-ND Creative Commons license.


% Start a document with the here given default font size and paper size.
\documentclass[10pt,a4paper]{article}

% Set the page margins.
\usepackage[a4paper,margin=0.75in]{geometry}

% Setup the language.
\usepackage[english]{babel}
\hyphenation{Some-long-word}

% Makes resume-specific commands available.
\usepackage{resume}




\begin{document}  % begin the content of the document
\sloppy  % this to relax whitespacing in favour of straight margins


% title on top of the document
\maintitle{Marvin Ouma}{Last update on \today}

\nobreakvspace{0.3em}  % add some page break averse vertical spacing

% \noindent prevents paragraph's first lines from indenting
% \mbox is used to obfuscate the email address
% \sbull is a spaced bullet
% \href well..
% \\ breaks the line into a new paragraph
\noindent\href{mailto:oumamarvin.at.gmail.dot.com}{oumamarvin\mbox{}@\mbox{}gmail.com}\sbull
\textsmaller{+}254.722901642\sbull
\href{https://github.com/pancakem}{github.com/pancakem}\sbull
\\
Nairobi \sbull
Kenya

\spacedhrule{0.9em}{-0.4em}  % a horizontal line with some vertical spacing before and after

\roottitle{Summary}  % a root section title

\vspace{-1.3em}  % some vertical spacing
\begin{multicols}{2}  % open a multicolumn environment
\noindent \emph{Entrepeneurial geek with roots in the open source movement. Passionately enabling software-related teams to deliver. Creates/\,structures/\,improves processes. Architects and helps to implement future-proof solutions.}
\\
\\
I started programming, purely, for class until I read \emph{C The
  Programming Language}. Since then I have taught myself system
administration and programming in a few languages. During my
exploration, I got introduced to the open source movement and I have
contributed to both personal and organization projects. I also have
gotten to experiment with micro-controllers and I am of the opinion
they are really fun.
\end{multicols}


\spacedhrule{0em}{-0.4em}

\roottitle{Experience}
\headedsection
  {\href{https://eacdirectory.co.ke}{EACDirectory}}
  {\textsc{Remote}} {%
  \headedsubsection
    {Systems Administration Intern}
    {Dec \apo20 -- Jan \apo21}
    {\bodytext{Trained on how to install, configure and administer
        popular web-based web hosting control panels. Wrote automation
        scripts in Bash and Python.
      }}
}

\headedsection
  {\href{http://www.littlekidogo.co.za}{Little Kidogo}}
  {\textsc{Nairobi, Kenya}} {%
  \headedsubsection
    {Embedded Systems Engineer}
    {May \apo20 -- Oct \apo20}
    {\bodytext{I developed and maintained drivers for a custom Rust
        kernel. Helped design and build a race timer trap with the
        ESP32 micro-controller. Involved in the building of a GraphQL
        service to report on the data from the ESP32 race timer trap.
      }}
}

\headedsection
  {\href{http://www.moot.co.ke}{Moot Insights}}
  {\textsc{Nairobi, Kenya}} {%
  \headedsubsection
    {Backend Engineer}
    {Sep \apo20 -- Aug \apo20}
    {\bodytext{Architected and built various micro-services; a few
        being a notification server and payment service with the
        M-Pesa gateway. Established test automation and continuous
        integration with Travis CI. Did extensive documentation of the
        developed systems.
      }
    }
}

\headedsection  % sets the header for the section and includes any subsections
  {\href{https://www.jkuat.ac.ke}{Jomo Kenyatta University of Agriculture and Technology}}
  {\textsc{Nairobi, Kenya}} {%
  \headedsubsection  % sets the header for a subsection and contains usually body text
    {Research Assistant}
    {Apr \apo19 -- Aug \apo19}
    {\bodytext{Placed in an AI research program where I was tasked
        with mining, analysis and categorization of data.
      }
    }
    }

\headedsection
{\href{http://www.littlekidogo.co.za}{Little Kidogo}}
  {\textsc{Remote}} {%
  \headedsubsection
    {Front-end Engineer Intern}
    {Sep \apo18 -- Apr \apo19}
    {\bodytext{My first internship experience, I was trained in web
        development using Elm. I became responsible for building web
        components and consuming back-end GraphQL resources in front-end projects.}}
}

\vspace{-0.2em}
%\begin{center}
 % \emph{\small Please refer to \href{}{} for a more complete list of work experience along with recommendations.}
%\end{center}


\spacedhrule{0.5em}{-0.4em}

\roottitle{Education}

\headedsection
  {\href{https://www.jkuat.ac.ke}{Jomo Kenyatta University of
Agriculture and Technology}}
  {\textsc{Nairobi, Kenya}} {%
  \headedsubsection
    {BSc in Computer Science}
    {2017 -- 2021}
    {}
}

\spacedhrule{0.5em}{-0.4em}

\roottitle{Skills}

\inlineheadsection  % special section that has an inline header with a 'hanging' paragraph
  {Technical expertise:}
  {Linux administration skills (e.g.\ Bash scripting,
    Apache/\acr{NGINX}, Postgres/My/No\acr{SQL}). Big
    fan of Agile methodologies, continuous delivery and functional
    programming.  Enjoys writing C/\nsp Python/\nsp Go/\nsp Elm/\nsp
    Haskell and some intermediate x86 assembly.  Solid knowledge of backend web technology stack. Well
    experienced with containerization (Docker).  Emacs user.
  }

\vspace{0.5em}
\inlineheadsection
  {Natural languages:}
  {Luo \emph{(mother tongue)}, Swahili \emph{(national language)}, English \emph{(full professional proficiency)}, German \emph{(beginner)}.}


\spacedhrule{1.6em}{-0.4em}

\roottitle{Interests}

\inlineheadsection
  {Non-exhaustive and in alphabetical order:}
  {art, comic books, emulation, functional programming, history, music, philosophy.}


\end{document}
